---
title: "Project 2"
output: html_notebook

---

Part 1
Load the data and answer the following questions:

How many survey participants were there?
What are the data types of each column?
What are the top 3 universities with the most survey participants?


```{r}
# First I import the file and I clean it and convert it in a table
library(janitor)
library(dplyr)
library(stringr)
library(tibble)
library(ggplot2)
library(tidyverse)
library(httr)
library(reshape2)

Conf_Survey <- clean_names(survey) %>% 
  as_tibble(rownames_to_column(survey, "id"))

#After I use Glimpse to see the table date 

glimpse(Conf_Survey)

# How many survey participants were there? 30
# WHat are the date types of each column? int,fct, fct, int, int, int,int, fct

# I then group universities and summarise their number to see the top 3 universities

Conf_Survey %>% 
  mutate(number=number_of_employees/number_of_employees) %>% 
  group_by(university) %>% 
  summarise(number=sum(number))

# What are the top 3 universities of participants? Delf, Eindhoven & Groningen

```

Part 2
Obtain a horizontal bar graph of the number of survey participants for the different positions given in the column Position.

```{r}
# I create a vector with the info related to the position of the participants to the survey


Position_bar <- Conf_Survey %>% 
mutate(number=number_of_employees/number_of_employees) %>% 
group_by(position) %>% 
summarise(number=sum(number))

# After I create the horizontal graph
ggplot(data=Position_bar, mapping = aes(x=position, y=number)) +
  geom_bar(stat="identity") +
  coord_flip() 

```

Part 3
Group the data in the column Number of employees in the following bins:

Small (0 to 10)
Medium (10 to 20)
Large (20 to 100)
Extra large(over 100)
Then plot a bar chart with {ggplot2} of the number of values in each of the bins.

```{r}


#First I group and arrange the date according to the Number of employees
# AfterI create the bar chart

Conf_Survey %>% 
  mutate(bins=case_when(number_of_employees <= 9 ~ "Small", number_of_employees <= 19 ~ "Medium", number_of_employees <= 99 ~ "Large", TRUE ~ "Extr large")) %>%
  arrange(number_of_employees) %>% 
  select(number_of_employees, bins) %>% 
  ggplot(mapping = aes(x= bins, y = number_of_employees)) +
  geom_bar(stat="identity") +
  labs(title="No. of Employees", subtitle="By Size", x="Bins", y="Number of Employees")

```


Part 4
Obtain a stacked horizontal bar plot with {ggplot2} that gives the percentage of employees that are Ph.D. students, postdocs and professors for each research group. Use a custom theme.

We have not covered , so you will have to study the documentation, and/or some blog posts. There is also a great book about {ggplot2} recipes that I recommend you check out: The hitchhiker guide to ggplot2. The book is pay-as-you-want, so select Package "The book" and choose a number from 0 and 30 dollars.

```{r}
# I create a new table only with the positions and I use mel to create a vairable.
# then I use ggplot to create the chart

Conf_Survey1 <- select(Conf_Survey, 1, 5,6,7)
Conf_Survey2 <- melt(Conf_Survey1, id.var="x")
ggplot(Conf_Survey2, aes(x = x, y = value, fill = variable)) +
  geom_bar(stat = "identity") + coord_flip() +
  labs(title = "No. of Employees by position", x = "No. of Employees", y = "Team")

```

