---
title: "Project 6"
output: html_notebook
---


```{r}

#  I write all libraries I will require

library(dplyr)
library(tidyverse)
library(tidyr)
library(httr)
library(purrr)
library(ggplot2)
library(reshape2)
library(stringr)


#After I import the date of the excel file

athletes <- read_excel("C:/Users/Ana/Desktop/Data50/Project 6/olympics.xlsx", sheet = "athletes") %>%
  rename(athlete_id = ID)
country <- read_excel("C:/Users/Ana/Desktop/Data50/Project 6/olympics.xlsx", sheet = "country")
games <- read_excel("C:/Users/Ana/Desktop/Data50/Project 6/olympics.xlsx", sheet = "games")
medals <- read_excel("C:/Users/Ana/Desktop/Data50/Project 6/olympics.xlsx", sheet = "medals")


# And then join the tables to have the names of the athletes

country_athlete <- left_join(country, athletes, by=c("athlete_id"))
medals_athlete <- left_join(medals, athletes, by=c("athlete_id"))


```

 Part 1
Have some athletes competed for different countries over time?

```{r}

country_athlete %>%
    select(athlete_id, Name, NOC) %>%
    group_by(athlete_id, Name) %>%
    filter(n() > 1, sum(duplicated(NOC)) == 0) %>%
    ungroup()

```


Part 2
Who are the ten athletes that took part in most games?

```{r}

# I then group by athlete_id and summarise the number of games.
# Finally I arrange it with desc

country_athlete %>% 
  mutate(number=athlete_id/athlete_id) %>% 
  group_by(Name) %>% 
  summarise(number=sum(number)) %>%
  arrange(desc(number)) %>%
  head(10)

```


Part 3
What athlete(s) kept a Gold medal for the longest time?

```{r}


gold <- select(medals_athlete, athlete_id, Games, Medal, Name) %>% 
  filter(Medal=="Gold") %>%
  mutate(number=athlete_id/athlete_id) %>% 
  group_by(Name) %>% 
  summarise(number=sum(number)) %>%
  arrange(desc(number))
gold %>%
  head(5)


```


Part 4
What country(ies) kept a Gold medal for the longest time?

```{r}

gold_country <- select(medals, athlete_id, Games, Medal, Team) %>% 
  filter(Medal=="Gold") %>%
  mutate(number=athlete_id/athlete_id) %>%
  group_by(Team) %>%
  summarise(number=sum(number)) %>%
  arrange(desc(number))
gold_country %>%
  head(5)
  

```


Part 5
Who are the ten athletes that competed in the most events (some athletes take part in more than one event during games) ?

```{r}

country_athlete %>% 
  mutate(number=athlete_id/athlete_id) %>% 
  group_by(Games, Name) %>% 
  summarise(number=sum(number)) %>%
  arrange(desc(number)) %>%
  head(10)


```


Part 6
Create a new table showing the number of medals per country (rows) and per year (column). Keep only the 15 countries with the most medals overall.


```{r}

medals_country <- select(medals, athlete_id, Games, Medal, Team) %>% 
  filter(Medal!="NA") %>%
  mutate(number=athlete_id/athlete_id) %>%
  group_by(Team, Games) %>%
  summarise(number=sum(number)) %>%
  arrange(desc(number)) 
  
top_15 <- medals_country %>% 
  tidyr::spread(Games, number, fill=0) 

total <- as.tibble(rowSums(top_15[,c(2:52)]))

country_top15 <- merge(top_15, total, by="row.names", all.x=TRUE) %>%
  arrange(desc(value)) 

country_top15%>%
  head(15)

```


Part 7
Create a scatterplot showing the average height and weight of competitors per sport (one dot per sport). Add labels with the sport names for:

the largest average height
the largest average weight
the smallest average height
the smallest average weight
the largest average BMI
the smallest average BMI
It might be that the same dot qualify for multiple labels. The formula to calculate Body Mass Index (BMI) is:
weight in kg / (height in meters)^2
 
 + geom_label(data=filter(plotathlete, ave_Weight %in% range(ave_Weight) | ave_Height %in% range(ave_Height) | bm %in% range(bm)), nudge_x = 1)
 
```{r}

#First I create the table with the date

plotathlete <- medals_athlete %>%  
  select(athlete_id, Event, Height, Weight) %>%
  group_by(Event, Height, Weight) %>%
  filter(Height!="NA", Weight!="NA") %>%
  group_by(Event) %>%
  mutate(ave_Weight = mean(Weight)) %>%
  mutate(ave_Height = mean(Height)) %>%
  mutate(bm = Weight/((Height/100)^2)) 

# I then create the plot with average weight, height and body mass

plota <- melt(plotathlete, id= c("ave_Weight", "ave_Height", "bm"))

plota1 <- ggplot(plota, aes(x=ave_Weight, y=ave_Height, colour=bm))  
  
plota1 + geom_point(shape=21) + labs(title="Average", subtitle="weight, height and body massPer Sport", x="Average Weight", y="Average Height", colour="Body Mass") 

# And finalle the plot with max and min values

#max_min <- mutate=range(plotathlete$ave_Weight))

```
 
```{r}



```
 

```{r}

plotathlete <- medals_athlete %>%  
  select(athlete_id, Event, Height, Weight) %>%
  group_by(Event, Height, Weight) %>%
  filter(Height!="NA", Weight!="NA") %>%
  group_by(Event) %>%
  mutate(Ave_Weight = mean(Weight)) %>%
  mutate(Ave_Height = mean(Height)) %>%
  mutate(Bm = Weight/((Height/100)*(Height/100)))

plotathlete %>% ggplot(aes(x=Ave_Weight, y=Ave_Height, label = Event)) + 
    geom_point(shape = 21, colour="green")  +
      labs(title="Average Weight, Height and Body Mass of Athletes", subtitle="Per Sport",
      x="Average Weight", y="Average Height", colour="Body Mass")

```


Part 8
Create a line plot showing the number of medals given by year (one line for Gold, one line for Silver and one line for Bronze). Does it change over time? Use facet to separate the medals at Summer games and Winter games.


```{r}
# I create first the table to do the line plot

type_medals <- medals %>% 
  separate(Games, c("Games", "Season"))%>%
  mutate_at(vars(Games), as.numeric) %>%
  select(athlete_id, Games, Season, Medal) %>%
  mutate(number=athlete_id/athlete_id) %>%
  filter(Medal!="NA") %>%
  arrange(Games, Medal, Season) %>%
  group_by(Games, Medal) %>%
  summarise(number=sum(number))%>%
  spread(key="Medal", value="number", fill=0) 

plot_medals <- melt(type_medals, id.vars = "Games")

lineplot <- ggplot(plot_medals, aes(x = Games, y = value, colour = variable))

lineplot + geom_line() + labs (title="Number of medals by year",
       x="Year", y="Number of Medals")

# Then I create the facet plot by season

type_medals1 <- medals %>% 
  separate(Games, c("Games", "Season"))%>%
  mutate_at(vars(Games), as.numeric) %>%
  select(athlete_id, Games, Season, Medal) %>%
  mutate(number=athlete_id/athlete_id) %>%
  filter(Medal!="NA") %>%
  arrange(Games, Medal, Season) %>%
  group_by(Games, Medal, Season) %>%
  summarise(number=sum(number))%>%
  spread(key="Medal", value="number", fill=0) %>%
  mutate(total=sum(Gold+Silver+Bronze))

type_medals1 %>% 
  ggplot(aes(x=Games, y=total)) + 
  geom_jitter() + 
  facet_wrap(~Season) + labs (title="Number of medals by year and Season",
       x="Year", y="Number of Medals")


```

