---
title: "Report No. 1"
output: html_notebook
---


```{r}
# First I import both files in the NoteBook
professors <- read.csv("C:/Users/Ana/Desktop/Data50/Project 1/professors.csv")
View(professors)
students <- read.csv("C:/Users/Ana/Desktop/Data50/Project 1/students.csv")
View(students)
# Then I clean-up the data of both files (professors & students)
library(readr)
library(janitor)
library(dplyr)
library(tibble)
library(tidyr)
# For Professors
professor_table <- as_tibble(rownames_to_column(professors, "id") )
professor_table1 <- clean_names(professor_table)
professor_tabl <- select(professor_table1, id, -x, prof_totally_disagree = totally_disagree, prof_disagree = disagree, prof_agree = agree, prof_totally_agree = totally_agree)
# for students
students_table <- as_tibble(rownames_to_column(students, "id") )
students_table1 <- clean_names(students_table)
students_tabl <- select(students_table1, id, -x, stud_totally_disagree = totally_disagree, stud_disagree = disagree, stud_agree = agree, stud_totally_agree = totally_agree)
# now I join both tables
id_table <- left_join(students_tabl, professor_tabl, by=c("id"))
```

Part No.1

What is the total number of answers obtained from students?
What is the total number of answers obtained from professors?
Does each question have the same number of answers?

```{r}
# To answer the first question, I create a new column to summarize the number ofanswers  given by the students and then I use sum to see the number.
id_table %>% 
  mutate(stud_answers = stud_totally_disagree + stud_disagree + stud_totally_agree + stud_agree) %>% 
  summarise(total_st_answers = sum(stud_answers))
# answer: 7748


# I do the same for the answers given by the professors
id_table %>% 
  mutate(prof_answers = prof_totally_disagree + prof_disagree + prof_totally_agree + prof_agree) %>% 
  summarise(total_prof_answers = sum(prof_answers))
# answer: 3654 

# For question no. 3, I summarize the number of answers per question in a new column and I pull the values
id_table %>% 
  mutate(all_answers = stud_totally_disagree + stud_disagree + stud_totally_agree + stud_agree + prof_totally_disagree + prof_disagree + prof_totally_agree + prof_agree) %>% 
  pull(all_answers)
# answer: no
```



Part 2
Obtain side-by-side bar charts comparing the distribution of answers of the students versus the professors for each question.

```{r}
# First I create a table only with the answers from Students and Professors
library(ggplot2)
library(dplyr)
New_Stud_table <- id_table %>% 
  mutate(stud_answers = stud_totally_disagree + stud_disagree + stud_totally_agree + stud_agree) 
New_prof_table <- id_table %>% 
  mutate(prof_answers = prof_totally_disagree + prof_disagree + prof_totally_agree + prof_agree) 
RWnew_stud_table <- select(New_Stud_table, id, stud_answers)
RWnew_prof_table <- select(New_prof_table, id, prof_answers)
Table <- left_join(RWnew_prof_table, RWnew_stud_table, by="id")
Table_vs <- Table %>% 
  select(everything()) %>% 
  mutate(all_answers = stud_answers + prof_answers)
# and finally I create the chart using gather and plot
Table_vs1 <- gather(Table_vs, event, total, prof_answers:stud_answers)
plot <- ggplot(Table_vs1, aes(id, total, fill=event))
plot <- plot + geom_bar(stat = "identity", position = 'dodge')
plot
```

Part 3
With Likert scale data, we cannot use the mean as a measure of central tendency as it has no meaning (i.e. what is the average of strongly agree and disagree?).

The most appropriate measure of central tendency is the mode. Compute the mode for the students and professors for each of the questions.

```{r}
#I create a vector with the total of answers given by students and professors to calculate the mode.
Prof_mode <- c(115, 115, 115, 115, 115, 115, 115, 115, 115, 115, 115, 115, 115, 115, 115,115, 115, 115, 115, 115, 115, 115, 115, 115, 115, 113, 112, 113, 111, 112, 115, 103)
names(table(Prof_mode))[table(Prof_mode)==max(table(Prof_mode))]
# Mode Professors answers: 115
 Stud_mode <- c(244, 244, 244, 244, 244, 244, 244, 244, 244, 244, 244, 244, 244, 244, 244,244, 244, 244, 244, 244,244, 244, 244, 244, 244, 233, 234, 239, 233, 241, 238, 230)
 names(table(Stud_mode))[table(Stud_mode)==max(table(Stud_mode))]
# Mode Students answers: 244

```



